Symmetry-based constraints on the size of the dynamical Solar neighborhood

### 2019-04-09 paper/ms.tex
Change neighborhood to dynamical neighborhood

\begin{figure*}
\plotone{fig/Rn_vs_mc.pdf}
\caption{The neighborhood around an open cluster of mass $m_c$ for the thin,
and thick orbits (\thincolor and \thickcolor, respectively; see
Table~\ref{tab:orbits}) and for each of the FIRE galaxies considered here ---
\mi{}, \mf{}, and \mm{} ({\em left}, {\em center}, and {\em right} panels,
respectively). Given the $z$ offset for a cluster of mass $m_c$ computed in
Figure~\ref{fig:cluster_offset}, we convert this to a chord length using the
result from Figure~\ref{fig:range_deltaphi}. We interpret this chord length as
the ``neighborhood'' around the cluster, i.e. the distance from the cluster
one could go before the $J_z$ error induced by our midplane effect is
comparable to the intrinsic action dispersion of the cluster. When the $z$
offset is larger than the maximum range in Figure~\ref{fig:range_deltaphi}, we
report the maximum chord length ($2\times8.2\,\kpc$). We aso report the same
procedure but using the $\pm1\sigma$ lines from
Figure~\ref{fig:range_deltaphi}, which we plot here as dashed lines. For the
thick orbit (\thickcolor), the neighborhood is quite large and thus the effect
is negligible. However, for the thin orbit (\thincolor), which is closest to
the orbits of nearby open clusters (see Table~\ref{tab:real_clusters}), the
neighborhood is only a few hundred $\pc$ for low-mass clusters.}
\label{fig:Rn_mc}
\end{figure*}

>>>>

\begin{figure*}
\plotone{fig/Rn_vs_mc.pdf}
\caption{The dynamical neighborhood (discussed in Section~\ref{sssec:neighborhood}) around an open cluster of mass $m_c$ for the thin-disk,
and thick-disk orbits (\thincolor{} and \thickcolor{}, respectively; see
Table~\ref{tab:orbits}) and for each of the FIRE galaxies considered here ---
\mi{}, \mf{}, and \mm{} ({\em left}, {\em center}, and {\em right} panels,
respectively). Given the $z$ offset for a cluster of mass $m_c$ computed in
Figure~\ref{fig:cluster_offset}, we convert this to a chord length using the
result from Figure~\ref{fig:range_deltaphi}. We interpret this chord length as
the ``neighborhood'' around the cluster, i.e. the distance from the cluster
one could go before the $J_z$ error induced by our midplane effect is
comparable to the intrinsic action dispersion of the cluster. When the $z$
offset is larger than the maximum range in Figure~\ref{fig:range_deltaphi}, we
report the maximum chord length ($2\times8.2\,\kpc$). We aso report the same
procedure but using the $\pm1\sigma$ lines from
Figure~\ref{fig:range_deltaphi}, which we plot here as dashed lines. For the
thick orbit (\thickcolor), the neighborhood is quite large and thus the effect
is negligible. However, for the thin orbit (\thincolor), which is closest to
the orbits of nearby open clusters (see Table~\ref{tab:real_clusters}), the
neighborhood is only a few hundred $\pc$ for low-mass clusters.}
\label{fig:Rn_mc}
\end{figure*}
